An agent-based model for city networks based on interactions between firms

### 2019-10-16 main.tex
Update on Overleaf.

@@

@@

Data sources:
\begin{itemize}
	\item ORBIS database for company links
	\item GHS UCDB for GDP of urban built-up areas
	\item Functional urban areas (JRC-EC) for consistent ontology and spatial join between the different sources
\end{itemize}

@@

More probably, we may have to work on an extract of the ORBiS database including only links from and to UK-based companies

@@

@@

>>>>

\cite{dai2016generative} simpler urban network generative model

@@

\subsection{Statistical analysis}

% TODO stat models justifying processes included:
% - poisson regression if we count a number of links?
% - country couples fixed effect to estimate the country distance matrix (as a function of interaction range ?)
% - multilevel modeling ?
% - distribution and properties (spatial stats ?) of sector distributions and similarities

@@

Data sources:
\begin{itemize}
	\item AMADEUS database for company links
	\item GHS UCDB for GDP of urban built-up areas
	\item Functional urban areas (JRC-EC) for consistent ontology and spatial join between the different sources
	\item Cities GDP can also be computed by aggregating company data: correlation between this approach and the GHS one must be checked
\end{itemize}

@@

More probably, we may have to work on an extract of the AMADEUS database including only links from and to UK-based companies. This constraints imposes modifications on the level to remain consistent:
\begin{itemize}
    \item the adjustment error can only be partial and computed on the UK links only
    \item an initialization method for the missing links must be implemented (e.g. through a statistical analysis? not far from the model then)
    \item the model can be run without initial links, and an additional parameter sets the duration necessary to reach the time considered as the first date
\end{itemize}

@@

The model is implemented in NetLogo and integrated into the OpenMOLE platform for model exploration \cite{reuillon2013openmole}.

@@

\subsection{Real application to Europe}

% Q: do we do some "hybrid experiments"? - ex synthetic system of cities but real sector distribution
